---
title: "Installing this package & getting help"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installing this package & getting help}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval =FALSE
)
```


## Intro

The goal of the researchcyclematrix package is

1. To not have to look at the RCM anymore. (Who picked that colour scheme)
1. Operate on the RCM directly from R
1. Streamline the process of keeping the matrix up to date & consistent

## Install

to install the researchcyclematrix package run

```{r}
devtools::install_github("mabafaba/researchcyclematrix", build_opts = c(), build_vignettes = TRUE)

```


## Documentation
Open the documentation:

```{r}
browseVignettes("researchcyclematrix")
```




## Troubleshooting the installation

1. Make sure you have R version >=3.5.3 You can check that with 

```{r}
version
```
If your version is older, delete R and download and install it again, or use `installr` package (might be a bit of a struggle though.)

2. Make sure you're on the latest version of devtools

```{r}

install.packages()
```

```{r setup}
library(researchcyclematrix)
```

## Contributing to the package
Read the [developer readme](https://github.com/mabafaba/researchcyclematrix) as an introduction to how this package is structured 
The best place to start contributing to this package is by checking the open [issues on github](https://github.com/mabafaba/researchcyclematrix/issues/) and join the conversation.
Its best to first leave a comment on the issue to start a conversation with the current maintainers before writing any code.




