---
title: "Prefilling the monthly research tracker"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Prefilling the monthly research tracker}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

## Quickstart

For this to work, you must have the "xlsx" package installed. (if xlsx doesn't work on your machine, see further instructions below)
Then just run this to load the package and prefill the tracker:

```{r}
library(researchcyclematrix)
rcm_prefill_research_tracker()
```

## custom target file

If you speficy a custom target file, the path needs to exist and the file needs to end with ".xlsx"
```{r}
researchcyclematrix::rcm_prefill_research_tracker(output_xlsx_file_name = "./myfolder/custom_output_filename.xlsx")
```

## Custom research cycle matrix

By default, the research cycle matrix will be downloaded from the google drive and used directly.
You can also use an RCM that was downloaded separately, for example to edit / subset it first:

```{r}
# download research cycle matrix:
rcm <- rcm_download()
# edit, for example take a subset (only reporting unit items):
rcm_reporting_only <- rcm[ rcm$unit == "reporting", ]
# create template

rcm_prefill_research_tracker(output_xlsx_file_name = "tracker_reporting.xlsx",
                             rcm = rcm_reporting_only)

```

## Outputting many trackers

With custom RCMs we can create many trackers for different subsets at once. For example for each country.

```{r}
# get first three letters country code from research cycle ID
rcm<-rcm_download()
rcm$country<-substr(rcm$rcid, 1, 3)
# split the rcm into a list of smaller rcms:

rcm_by_country<- split.data.frame(rcm,rcm$country)

output_xlsx_file_name <- paste0("tracker_",names(rcm_by_country),"_", Sys.Date(),".xlsx")

# use the "purrr" package to do something many times (purrr::map) and make sure it doesn't stop if an iteration fails (purrr::possibly):
library(purrr)
# run the function on each country / each part of the rcm and create tracker files
safe_rcm_prefill_research_tracker <- possibly(rcm_prefill_research_tracker,otherwise = "couldn't write xlsx file.")
purrr::map2(output_xlsx_file_name,
            rcm_by_country,
            safe_rcm_prefill_research_tracker)


```
## If xlsx doesn't work / JAVA related problems

If the xlsx package is not installed or does not work due to JAVA issues, we can give you just the prefilled rows data frame. You need to write that to a csv file and copy/paste it into the template yourself.

```{r}
# get rows only without trying to read/write xlsx:
prefill_data <- rcm_prefill_research_tracker(use_xlsx_package = FALSE)
# write to file:
write.csv(prefill_data, "prefill_data.csv")
# open the file:
browseURL("prefill_data.csv")
#... now copy the rows.
```



